% Version 2.21 of 2022/01/12
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subcaption}
\usepackage{footnote}


% mathbb font
\usepackage{amssymb}
% C++ code
\usepackage{color}
\usepackage{listings}
\lstset{ %
language=C++,                % choose the language of the code
basicstyle=\small\ttfamily,       % the size of the fonts that are used for the code \footnotesize
numbers=left,                   % where to put the line-numbers
numberstyle=\small\ttfamily,      % the size of the fonts that are used for the line-numbers \footnotesize
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=single,           % adds a frame around the code
tabsize=2,          % sets default tabsize to 2 spaces
captionpos=b,           % sets the caption-position to bottom
breaklines=true,        % sets automatic line breaking
breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}{*)},          % if you want to add a comment within your code
numberbychapter={false}         % default true
}
% fig
\captionsetup{compatibility=false}
%
\begin{document}
%
\title{EasyCompare: Performance Analysis System for GNN Training across GPUs}


%\author{Kejie Ma\inst{1}$\dagger$ \and Zizheng Zhang\inst{1}$\dagger$ \and Qingxiao Sun\inst{1} \and Hailong Yang\inst{1}\thanks{Corresponding author, hailong.yang@buaa.edu.cn} \and \\ Zhongzhi Luan\inst{1} \and Depei Qian\inst{1}}
%\authorrunning{K. Ma, Z. Zhang et al.}
%\institute{School of Computer Science and Engineering, Beihang University, Beijing, China
%\email{\{19373449,cpyking,qingxiaosun,hailong.yang,07680,depeiq\}@buaa.edu.cn}}
%
%\def\thefootnote{$\dagger$}\footnotetext{Equal contribution}\def\thefootnote{\arabic{footnote}}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Over the years, Graph Neural Networks (GNNs) have attracted widespread attention. The factors affecting GNN performance include framework designs and GPU architectures. However, it is challenging to compare GNN frameworks fairly due to inconsistent language styles. In addition, deploying GNN models on diverse GPUs requires significant engineering efforts. To this end, we propose EasyCompare, an integrated system for efficient GNN performance comparison and result analysis. EasyCompare incorporates the GUC Domain Specific Language (DSL) to unify the language styles and achieve functionally equivalent code transformation. EasyCompare also provides front-end interaction to deploy GNN models and visualize performance logs automatically. We conduct extensive experiments to compare the performance of various GNN models between frameworks and GPUs. The insights from experimental results can help researchers explore optimization paths for adapting GNN frameworks to GPU architectures.

  \keywords{GNN \and GPU \and Code Generation \and Performance Analysis}
\end{abstract}
%
%
%
\input{introduction.tex}
\input{background.tex}
\input{gnn_dsl.tex}
\input{code_transformer.tex}
\input{system_design.tex}
\input{experiment.tex}
\input{conclusion.tex}
%
%
%
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}
\bibliography{mybibliography}
\end{document}
